### 2024-03-19 Scripts/Manuscript/manuscript.Rmd
fixed compiling errors and plot 456 and table 1 look.

appendix:
  - "Scripts/AppendixScripts/Appendix_pre-reg_analyses.Rmd"
  - "Scripts/AppendixScripts/Appendix_multilevel_analyses.Rmd"
  - "Scripts/AppendixScripts/Appendix_omega_analyses.Rmd"
  - "Scripts/AppendixScripts/Appendix_initial_QMP_analyses.Rmd"

classoption       : "man"
output            : papaja::apa6_pdf
knit              : worcs::cite_all
bibliography: references.bib
---

@@

# loading source script
source(file = "C:/Users/u686785/OneDrive - Tilburg University/Documents/uvt/PHD/Master Thesis to Paper/Reproducible_R_Project/Scripts/source_script.R")

@@

Greater score-reliability means greater consistency in estimation as variance around the estimate of the true effect is decreased. Consequently measures across different occasions, including between original and replication, should also become more consistent [@nunnaly1994assessment]. When original and replication research share consistent result, and as long as the studied effect is true, then on average their statistical conclusions should converge.

@@

The total number of identified psychological findings for which replication was attempted across the four included Many Labs projects amounts to a total of `r sum(table(coded_data_replications$many_labs_version, coded_data_replications$appearance)[,1])`. Each finding was tested across several labs, and was related to a finding from an original study, the combination of all these studies and their associated information formed a replication set. For each research finding, any primary measures assessing a unique variable were taken to form the key unit of analysis. Here primary measures refers to measures assessing variables included in the primary test of the replication. This was done to ensure that the analyses could link directly to the replicability of a study. Acquiescence bias checks, manipulation checks, measures used for pilot testing, and measures added for exploratory analyses in replication studies were not included. The result was a total sample size of `r nrow(coded_data_replications)` measures used in both original and replication research [^1]. Table BELOW shows further descriptive information about the data for each Many Labs Project.

@@

# Changing column names to be less computer speak-y looking
colnames(many_labs_descriptives_table) <- c("Many Labs Version", "N ML Projects", "N Primary Measures",
                                            "Replication Total N", "Replication Total IQR", "Original Total N", 
                                            "Original Total IQR")

# print the table in apa formatting
apa_table(
  many_labs_descriptives_table, align = c("l", "r", "r", "r", "r", "r", "r")
  , caption = "Descriptive information of number of included projects measures, and their sample size, across many labs projects for both original articles and replication protocols"
  , escape = FALSE, placement = "htp", midrules = 4)

@@

When comparing the reported reliabilities with the calculated reliabilities displayed in figure \@ref(fig:Plot23AlphaCode), all but `r apa_num(sum(plot_23_data_reported_alpha$coefficient_difference > 0), numerals = FALSE)` of the reported reliabilities are in the lower half of the distribution of the calculated reliabilities within their own measure. However when looking across the measures, the mean of the distribution of the calculated coefficients of all but `r apa_num(sum(aggregate(plot_23_data_alpha_reordered$alpha, list(plot_23_data_alpha_reordered$g), FUN = mean)[plot_23_data_reported_alpha$article_order,2] <= mean(data_h3_multiple$alpha)), numerals = FALSE)` of the measures that have reported reliability coefficients is larger than the mean calculated Cronbach's alpha.

@@

# data re-ordering (was not saved in export)
plot_23_data_alpha_reordered <- data_prep_plot_23_alpha(plot_23_data_alpha)

@@

In order to visualize the results on QMPs, the proportions of the QMP ratio obtained for each QMP type (see Table \@ref(tab:QMPCodingInfoTable)) are shown across the top layer of Figure \@ref(fig:Plot456Code) for both replication protocols and original articles. While in the bottom layer of Figure \@ref(fig:Plot456Code) the overlayed distributions of the total QMP ratios from the replication protocols and original studies are displaued, with dots indicating each datapoint, and the line indicating the mean for either distribution. A large number of QMP ratios are missing for the QMP modification type , because only `r apa_num(table(coded_data_replications$mod_check)["True"])` out of `r apa_num(length(coded_data_replications$mod_check))` measures in replications, and only `r apa_num(table(coded_data_original_shortened$mod_check)["True"], numerals = FALSE)` measures used in original studies were modified.

```{r Plot456Code, warning = FALSE, fig.cap = "QMP ratio counts for each QMP Type and QMP total ratio distribution grouped by whether the QMP ratio was obtained from an original article or a replication protocol. The top row shows for each QMP type the proportions of each QMP ratio obtained, darker colours represent proportionally more QMPS, grey means modification did not occur for that measure. The bottom graph shows the distributions of total QMP ratios for both replication protocols and original articles, with the line indicating the mean QMP ratio. The specific observed values are indicated along the bottom row with dots"}
# re-ordering the QMP-types, because it didn't save
plot_456_data$QMP_type <- factor(plot_456_data$QMP_type, levels = c("Definition", "Selection", "Operationalization", "Quantification", "Modification", "Total"))

### ratio (REV) Original and Rep
Plot_456_1 <- ggplot(plot_456_data[plot_456_data$QMP_type != "Total",], 
                      aes(x = RepOrg, fill = as.factor(QMP_ratio_1_REV))) + 
  geom_bar(position = "fill") +
  theme_minimal() +
  scale_fill_manual(values = c("#ff766c", "#ef6f65", "#ce5f57", "#be5851", "#aa4f48", "#994741", "#803b36", "#672f2b", "#562824", "#411e1b", "#341816", "#030101","#4366ff", "#4265fc", "#3551cb", "#324dc1", "#324cbe", "#2d44aa", "#2c44a9", "#283d99", "#223380", "#162255", "#10193e", "#010206", "#000102")) +
  theme(legend.position = "none") +
  facet_grid(~ QMP_type) + 
  ylab("Relative Prevalence of\nQMP Ratio in Sample") +
  xlab("QMP Type") +
  ggtitle("QMP Ratio's Per QMP Type Grouped by Original and Replication")

Mean_Rat_Rep <- mean(plot_456_data$QMP_ratio_REV[
  plot_456_data$QMP_type == "Total" & plot_456_data$RepOrg == "Replication"])
Mean_Rat_Org <- mean(plot_456_data$QMP_ratio_REV[
  plot_456_data$QMP_type == "Total" & plot_456_data$RepOrg == "Original"])

Plot_456_2 <- ggplot(plot_456_data[plot_456_data$QMP_type == "Total",], 
       aes(x = QMP_ratio_REV, fill = RepOrg, colour = RepOrg)) +
  geom_density(alpha = 0.2) +
  geom_point(y = 0, alpha = 0.2, size = 3) +
  geom_segment(aes(x = Mean_Rat_Rep, xend = Mean_Rat_Rep, y = 0, yend = 2.66)
               , color = "blue4") +
  geom_segment(aes(x = Mean_Rat_Org, xend = Mean_Rat_Org, y = 0, yend = 2.183)
               , color = "brown") +
  coord_cartesian(xlim = c(0, 1)) +
  theme_ridges() + 
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
  scale_fill_manual(values=c("brown", "blue4")) +
  scale_color_manual(values=c("brown2", "blue")) +
  scale_x_continuous(breaks = c(0, Mean_Rat_Rep, 0.25, Mean_Rat_Org, 
                                0.5, 0.75, 1), 
                     labels = c("0", "0.18", "0.25", "0.31", "0.5", 
                                "0.75", "1")) + 
  ggtitle("Distribution of Total QMP Ratio's by Original and Replication") +
  guides(color = "none") +
  labs(fill = "Coded from") +
  ylab("") +
  xlab("")

# combine both plots into one figure
grid.arrange(Plot_456_1, 
             Plot_456_2, 
             nrow = 2)

@@

## Risky Measurement Usage
This study assessed the quality of measurement and measurement reporting in original and replication research by investigating the quality of measurement in the Many Labs projects, and the original articles they attempted to replicate. Findings were in line with similar investigations in the literature by @shaw2020measurement & @flake2022construct. These two studies found that validity evidence and reliability coefficient reporting for measures was lacking in replications and original studies. This is illustrated in our sample by the fact that reliability coefficients were reported in too small quantity to conduct the planned analysis for hypothesis 1, and because of the `r nrow(coded_data_replications)` measures only `r sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")` measures in original articles and `r sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")` in replication protocol reported any validity evidence. Thus, reliability and validity evidence was underreported in our sample similarly to the findings of @shaw2020measurement, @flake2017construct & @flake2022construct, a problem that has also been addressed in earlier literature on this topic [@vacha1999practices; @green2011recent].

@@

>>>>

classoption       : "man"
output            : papaja::apa6_pdf
knit              : worcs::cite_all
---

@@

# loading source script
source(file = "../source_script.R")

@@

Greater score-reliability means greater consistency in estimation as variance around the estimate of the true effect is decreased. Consequently measures across different occasions, including between original and replication, should also become more consistent [@nunnally1994assessment]. When original and replication research share consistent result, and as long as the studied effect is true, then on average their statistical conclusions should converge.

@@

The total number of identified psychological findings for which replication was attempted across the four included Many Labs projects amounts to a total of `r sum(table(coded_data_replications$many_labs_version, coded_data_replications$appearance)[,1])`. Each finding was tested across several labs, and was related to a finding from an original study, the combination of all these studies and their associated information formed a replication set. For each research finding, any primary measures assessing a unique variable were taken to form the key unit of analysis. Here primary measures refers to measures assessing variables included in the primary test of the replication. This was done to ensure that the analyses could link directly to the replicability of a study. Acquiescence bias checks, manipulation checks, measures used for pilot testing, and measures added for exploratory analyses in replication studies were not included. The result was a total sample size of `r nrow(coded_data_replications)` measures used in both original and replication research [^1]. Table \@ref(tab:ManyLabsDescriptivesTable) shows further descriptive information about the data for each Many Labs Project.

@@

# Adding column names to the table for readability
colnames(many_labs_descriptives_table) <- c("ML Version", "N Projects", "N measures$^a$", "Rep. N", "Rep. IQR", "Org. N", "Org. IQR")

### failed table
# colnames(many_labs_descriptives_table) <- c("Version", "Projects", "Measures", "Total N", "Total IQR", "Total N", "Total IQR")

# c("", "N ML", "N Primary", "Replication", "Replication", "Original", "Original")

# kableExtra::kbl(many_labs_descriptives_table, align = c("l", "r", "r", "r", "r", "r", "r"), escape = FALSE, placement = "htp", row.names = FALSE) %>%
#   kableExtra::kable_classic( full_width = FALSE) %>%
#   kableExtra::add_header_above(c("Many Labs" = 1, "N ML" = 1, "N Primary" = 1, "Replication" = 1, "Replication" = 1, "Original" = 1, "Original" = 1), line = FALSE) %>% 
#   kableExtra::row_spec(4, extra_latex_after = "\\cmidrule(l{3pt}r{3pt}){2-5}")

# midrule wouldn't add ):<

# print the table in apa formatting
apa_table(
  many_labs_descriptives_table, align = c("l", "r", "r", "r", "r", "r", "r"), escape = FALSE, placement = "htp", midrules = 4, caption = "General Descriptives of the Many Labs Projects"
  , note = "$^a$ refers only to the number of identified primary measures, which this study is concerned with. Rep. = Replicaiton, Org. = Original., N = number of, IQR = Interquartile range.")
```

@@

```{r  ReorderPlot23Data}
# data re-ordering (factor order was not saved in export)
plot_23_data_alpha_reordered <- data_prep_plot_23_alpha(plot_23_data_alpha)
```

When comparing the reported reliabilities with the calculated reliabilities displayed in figure \@ref(fig:Plot23AlphaCode), all but `r apa_num(sum(plot_23_data_reported_alpha$coefficient_difference > 0), numerals = FALSE)` of the reported reliabilities are in the lower half of the distribution of the calculated reliabilities within their own measure. However when looking across the measures, the mean of the distribution of the calculated coefficients of all but `r apa_num(sum(aggregate(plot_23_data_alpha_reordered$alpha, list(plot_23_data_alpha_reordered$g), FUN = mean)[plot_23_data_reported_alpha$article_order,2] <= mean(data_h3_multiple$alpha)), numerals = FALSE)` of the measures that had a reported reliability coefficient was larger than the mean calculated Cronbach's alpha.

@@

@@

In order to visualize the results on QMPs, the proportions of the QMP ratio obtained for each QMP type (see Table \@ref(tab:QMPCodingInfoTable)) are shown across the top layer of Figure \@ref(fig:Plot456Code) for both replication protocols and original articles. While in the bottom layer of Figure \@ref(fig:Plot456Code) the overlayed distributions of the total QMP ratios from the replication protocols and original studies are displayed, with dots indicating each datapoint, and the line indicating the mean for either distribution. A large number of QMP ratios are missing for the QMP modification type , because only `r apa_num(table(coded_data_replications$mod_check)["True"])` out of `r apa_num(length(coded_data_replications$mod_check))` measures in replications, and only `r apa_num(table(coded_data_original_shortened$mod_check)["True"], numerals = FALSE)` measures used in original studies were modified.

```{r Plot456Code, warning = FALSE, fig.cap = "QMP ratio counts for each QMP Type and QMP total ratio distribution grouped by whether the QMP ratio was obtained from an original article or a replication protocol. The top row shows for each QMP type the proportions of each QMP ratio obtained, darker colours represent proportionally more QMPS, grey means modification did not occur for that measure. The bottom graph shows the distributions of total QMP ratios for both replication protocols and original articles, with the line indicating the mean QMP ratio. The specific observed values are indicated along the bottom row with dots"}

# re-ordering the QMP-types, because it didn't save
plot_456_data$QMP_type <- factor(plot_456_data$QMP_type, levels = c("Definition", "Selection", "Operationalization", "Quantification", "Modification", "Total"))

# shortening the replication and original labels for nicer plot 1
levels(plot_456_data$RepOrg) <- c("Org.", "Rep.")

### ratio (REV) Original and Rep
# QMP type specific QMP ratios
Plot_456_1 <- ggplot(plot_456_data[plot_456_data$QMP_type != "Total",], 
                      aes(x = RepOrg, fill = as.factor(QMP_ratio_1_REV))) + 
  geom_bar(position = "fill") +
  theme_minimal() +
  scale_fill_manual(values = c("#ff766c", "#ef6f65", "#ce5f57", "#be5851", "#aa4f48", "#994741", "#803b36", "#672f2b", "#562824", "#411e1b", "#341816", "#030101","#4366ff", "#4265fc", "#3551cb", "#324dc1", "#324cbe", "#2d44aa", "#2c44a9", "#283d99", "#223380", "#162255", "#10193e", "#010206", "#000102")) + # gradient for the colors was found by changing the brightness of the colour in a hsl color editor (in GIMP) to be equal to the inverse of the QMP ratio value.
  facet_grid(~ QMP_type) + 
  theme(legend.position = "none", strip.text = element_text(size = 7)) +
  ylab("Relative Prevalence of\nQMP Ratio in Sample") +
  xlab("QMP Type") +
  ggtitle("QMP Ratio's Per QMP Type Grouped by Original and Replication")

# changing the replication and original labels back for plot 2
levels(plot_456_data$RepOrg) <- c("Original", "Replication")

# calculating mean total QMP ratios
Mean_Rat_Rep <- mean(plot_456_data$QMP_ratio_REV[
  plot_456_data$QMP_type == "Total" & plot_456_data$RepOrg == "Replication"])
Mean_Rat_Org <- mean(plot_456_data$QMP_ratio_REV[
  plot_456_data$QMP_type == "Total" & plot_456_data$RepOrg == "Original"])

# total QMP ratios
Plot_456_2 <- ggplot(plot_456_data[plot_456_data$QMP_type == "Total",], 
       aes(x = QMP_ratio_REV, fill = RepOrg, colour = RepOrg)) +
  geom_density(alpha = 0.2) +
  geom_point(y = 0, alpha = 0.2, size = 3) +
  geom_segment(aes(x = Mean_Rat_Rep, xend = Mean_Rat_Rep, y = 0, yend = 2.66)
               , color = "blue4") +
  geom_segment(aes(x = Mean_Rat_Org, xend = Mean_Rat_Org, y = 0, yend = 2.183)
               , color = "brown") +
  coord_cartesian(xlim = c(0, 1)) +
  theme_ridges() + 
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
  scale_fill_manual(values=c("brown", "blue4")) +
  scale_color_manual(values=c("brown2", "blue")) +
  scale_x_continuous(breaks = c(0, Mean_Rat_Rep, 0.25, Mean_Rat_Org, 
                                0.5, 0.75, 1), 
                     labels = c("0", "0.18", "0.25", "0.31", "0.5", 
                                "0.75", "1")) + 
  ggtitle("Distribution of Total QMP Ratio's by Original and Replication") +
  guides(color = "none") +
  labs(fill = "Coded from") +
  ylab("") +
  xlab("")

## the following two plots are constructed solely for the purpose of extracting
# a legend from them.
for_legend_plot_456_org <- ggplot(plot_456_data[plot_456_data$QMP_type != "Total",], 
                                  aes(x = RepOrg, y = abs(QMP_ratio_REV - 1), fill = abs(QMP_ratio_REV - 1))) + 
  geom_bar(stat = "identity") +
  theme_minimal() +
  scale_fill_gradient(name = "Original", low = "#030101", high = "#ff766c", limits = c(0, 1), 
                      breaks = c(0.001, 0.5, 0.999), labels = c(1, 0.5, 0)) +
  theme(legend.title=element_text(size = 9)) + 
  facet_grid(~ QMP_type)

for_legend_plot_456_rep <- ggplot(plot_456_data[plot_456_data$QMP_type != "Total",], 
                                  aes(x = RepOrg, y = abs(QMP_ratio_REV - 1), fill = abs(QMP_ratio_REV - 1))) + 
  geom_bar(stat = "identity") +
  theme_minimal() +
  scale_fill_gradient(name = "Replication", low = "#000102", high = "#4366ff", limits = c(0, 1), 
                      breaks = c(0.001, 0.5, 0.999), labels = c(1, 0.5, 0)) +
  theme(legend.title=element_text(size = 9)) + 
  facet_grid(~ QMP_type)

# extracting the legends from the plot
legend_456_org <- get_legend(for_legend_plot_456_org) 
legend_456_rep <- get_legend(for_legend_plot_456_rep)

# combining both plots and the legends into one figure
grid.arrange(Plot_456_1, 
             Plot_456_2, 
             legend_456_org,
             legend_456_rep,
             layout_matrix = rbind(c(1, 3, 4),
                                    c(2, 2, 2)),
              widths = c(8, 1, 1))

@@

## Risky Measurement Usage
This study assessed the quality of measurement and measurement reporting in original and replication research by investigating the quality of measurement in the Many Labs projects, and the original articles they attempted to replicate. Findings were in line with similar investigations in the literature by @shaw2020measurement & @flake2022construct. These two studies found that validity evidence and reliability coefficient reporting for measures was lacking in replications and original studies. This is illustrated in our sample by the fact that reliability coefficients were reported in too small quantity to conduct the planned analysis for hypothesis 1, and because of the `r nrow(coded_data_replications)` measures only `r sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")` measures in original articles and `r sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")` in replication protocol reported any validity evidence. Thus, reliability and validity evidence was underreported in our sample similarly to the findings of @shaw2020measurement, @flake2017construct, and @flake2022construct, a problem that has also been addressed in earlier literature on this topic [@vacha1999practices; @green2011recent].

@@

# (APPENDIX) Appendix {-}

```{r child = "AppendixScripts/Appendix_pre-reg_analyses.Rmd"}
```

```{r child = "AppendixScripts/Appendix_multilevel_analyses.Rmd"}
```

```{r child = "AppendixScripts/Appendix_omega_analyses.Rmd"}
```

```{r child = "AppendixScripts/Appendix_initial_QMP_analyses.Rmd"}
```
